Effectful Semantics for Substructural SSA

### 2023-11-01 pldi24/paper.tex
Tap

@@

In this paper, we give a type-theoretic account of SSA-style programs, which we extend with support for substructural types. This allows us to perform proofs and inductive definitions over SSA programs much more easily, which we take advantage of to give SSA a categorical semantics in terms of distributive effectful categories equipped with an Elgot structure. We then give some models, and prove various optimizations sound on them.

@@

>>>>

\TODO{abstract?}

@@

\TODO{write about ``what is SSA", article style}

\TODO{basic blocks, strange scoping rules...}

@@

\section{Separation Logic}

\TODO{State transformer on traces}

\TODO{Monoidal functor, yielding sliding}
